Stock enhancement undermines community stability

### 2022-02-03 rmd/supporting_info.Rmd
edit: title page

**Time-series data.** We assembled time-series fish data at `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan. The Hokkaido Research Organization leads a long-term monitoring program at these watersheds, and the data are published as annual reports [@salmonandfreshwaterresearchinstituteAnnualReportMonitoring2021]. The program began in 1963, but an effective, standardized sampling method has been implemented since 1999 (two-pass sampling with a combination of electrofishing and cast net). Most data were collected in summer with irregular interannual intervals (1- to 3-year intervals for most cases), and sampling efforts were quantified by sampling area (average: `r op(mean(df_area$area))` $\pm$ `r op(sd(df_area$area))` m^2^). We confined our analysis to the sites that meet the following criteria: (i) the observation span (from the first to the last year of observation) exceeds 10 years, (ii) the number of observation years exceeds five years, and (iii) masu salmon is observed at least twice during the observation period. As a result, we used time-series data at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` watersheds from 1999 to 2019. Summed abundance of first and second passes was used in the following analysis. **Table S5** summarizes observed species in these watersheds.

>>>>

**Time-series data.** We assembled time-series fish data at `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan. The Hokkaido Research Organization leads a long-term monitoring program at these watersheds, and the data are published as annual reports [@salmonandfreshwaterresearchinstitutehokkaidoresearchorganizationAnnualReportMonitoring2021]. The program began in 1963, but an effective, standardized sampling method has been implemented since 1999 (two-pass sampling with a combination of electrofishing and cast net). Most data were collected in summer with irregular interannual intervals (1- to 3-year intervals for most cases), and sampling efforts were quantified by sampling area (average: `r op(mean(df_area$area))` $\pm$ `r op(sd(df_area$area))` m^2^). We confined our analysis to the sites that meet the following criteria: (i) the observation span (from the first to the last year of observation) exceeds 10 years, (ii) the number of observation years exceeds five years, and (iii) masu salmon is observed at least twice during the observation period. As a result, we used time-series data at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` watersheds from 1999 to 2019. Summed abundance of first and second passes was used in the following analysis. **Table S5** summarizes observed species in these watersheds.

### 2022-02-03 rmd/title.tex
edit: SI
Update title.tex
edit: title page

%\begin{titlepage}
\begin{flushleft}
\LARGE{\textbf{Supporting Information for: \newline Selective stock enhancement undermines community stability}}\\
\vspace*{\baselineskip}
\large{Akira Terui$^{*,1}$, Hirokazu Urabe$^2$, Masayuki Senzaki$^3$, Bungo Nishizawa$^4$}\\
\vspace*{1\baselineskip}
\normalsize{*Corresponding author \newline Email: hanabi0111@gmail.com}\\
\vspace*{1\baselineskip}
\normalsize{
$^1$ Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA \newline
$^2$ XXX \newline
$^3$ XXX \newline
$^4$ XXX}\\
\vspace*{2\baselineskip}
\textbf{This PDF file includes:}
\begin{itemize}
\item Supplementary text
\item XX
\item XX
\item SI References
\end{itemize}
\end{flushleft}
% \end{titlepage}

>>>>

%\begin{titlepage}
\begin{center}
\LARGE{\textbf{Supplementary Materials for:}}\\[7.5mm]
\LARGE{Stock enhancement undermines community stability}\\[7.5mm]
\large{Akira Terui, Hirokazu Urabe, Masayuki Senzaki, Bungo Nishizawa}\\[7.5mm]
\large{Correspondence to: hanabi0111@gmail.com}\\[15mm]
\end{center}
\begin{flushleft}
\textbf{This PDF file includes:}
\begin{itemize}
\item Materials and Methods
\item Supplementary text
\item Tables S1-10
\item Figures S1-S15
\item References
\end{itemize}
\end{flushleft}
% \end{titlepage}
